---
title: "Portfolio"
author: "Sidney Francis"
date: "14/02/2021"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: default

---

```{r, libaries}
library(spotifyr)
library(ggplot2)
library(plotly)
library(tidyverse)
library(usethis)
library(remotes)
library(flexdashboard)
library(compmus)
library(cowplot)
library(gridExtra)
```
```{r, circs, echo=FALSE}
circshift <- function(v, n) {
  if (n == 0) v else c(tail(v, n), head(v, -n))
}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )
```

```{r, sixties, echo=FALSE}
playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DXaKIA8E7WcJj')
sixties<- 
get_playlist_audio_features(playlist_username, playlist_uris)

playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DWTJ7xPn4vNaz')
seventies<- get_playlist_audio_features(playlist_username, playlist_uris)

playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DX4UtSsGT1Sbe')
eighties<-  get_playlist_audio_features(playlist_username, playlist_uris)

playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DXbTxeAdrVG2l')
nineties<- get_playlist_audio_features(playlist_username, playlist_uris)

playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DX4o1oenSJRJd')
thousands<- get_playlist_audio_features(playlist_username, playlist_uris)

playlist_username <- 'spotify'
playlist_uris <- c('37i9dQZF1DX5Ejj0EkURtP')
tens<- get_playlist_audio_features(playlist_username, playlist_uris)
```


```{r, top20, echo= FALSE}
top20 <-
  sixties %>% top_n(20, danceability) %>%
  mutate(country = "The 60s") %>%
  bind_rows(seventies %>% top_n(20, danceability) %>% mutate(country = "The 70s")) %>%
  bind_rows(eighties %>% top_n(20, danceability) %>% mutate(country = "The 80s")) %>% 
  bind_rows(nineties %>% top_n(20, danceability) %>% mutate(country = "The 90s")) %>%
  bind_rows(thousands %>% top_n(20, danceability) %>% mutate(country = "The 00s")) %>%
  bind_rows(tens %>% top_n(20, danceability) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )
```

```{r, TOP1, echo=FALSE}
top1 <-
  sixties %>% top_n(1, energy) %>%
  mutate(country = "The 60s") %>%
  bind_rows(seventies %>% top_n(1, energy) %>% mutate(country = "The 70s")) %>%
  bind_rows(eighties %>% top_n(1, energy) %>% mutate(country = "The 80s")) %>% 
  bind_rows(nineties %>% top_n(1, energy) %>% mutate(country = "The 90s")) %>%
  bind_rows(thousands %>% top_n(1, energy) %>% mutate(country = "The 00s")) %>%
  bind_rows(tens %>% top_n(1, energy) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )
```

```{r, top150, echo=FALSE}
top150 <-
  sixties %>% top_n(150, tempo) %>%
  mutate(country = "The 60s") %>%
  bind_rows(seventies %>% top_n(150, tempo) %>% mutate(country = "The 70s")) %>%
  bind_rows(eighties %>% top_n(150, tempo) %>% mutate(country = "The 80s")) %>% 
  bind_rows(nineties %>% top_n(150, tempo) %>% mutate(country = "The 90s")) %>%
  bind_rows(thousands %>% top_n(150, tempo) %>% mutate(country = "The 00s")) %>%
  bind_rows(tens %>% top_n(150, tempo) %>% mutate(country = "The 10s")) %>%
  mutate(
    country = fct_relevel(country, "The 10s", "The 00s", "The 90s", "The 80s", "The 70s", "The 60s")
  )
```


### Plan
Which decade of modern music (60s - 10s) Is the most suitable to party? In other words what was the party decade?
We will determine this by comparing multiple playlists based on energy, danceability and tempo.

We will use Spotify made playlists of all decades (given the fact that the algorithm is also made by Spotify this seemed fitting).

Playlists used:

- All out 60s 
- All out 70s
- All out 80s
- All out 90s
- All out 00s
- All out 10s
- And because it is just 2021 we will not include the 2020s. 

***
For some reason I'm unable to display more than one Key-, Chordo-, Chromagram without them overlapping.

### Quickest decade
First we will be looking at the tempi of all songs for each decade. Then we will make tempograms for the most popular track from each decade.
```{r, tempo_histogram, echo=FALSE}


sixties_hista<- 
hist(sixties$tempo, main = "Tempi in the 60s",
     xlab = "Tempo (BPM)",
     border="black", 
     col="blue", 
     xlim=c(50,250),
     ylim = c(0, 60),
     freq = TRUE)

seventies_hista<-
  hist(seventies$tempo, main = "Tempi in the 70s",  xlab = "Tempo (BPM)",
       border="black", 
     col="blue", 
     xlim=c(50, 250),
    ylim = c(0, 60),
     freq = TRUE)

eighties_hista<-
   hist(eighties$tempo, main = "Tempi in the 80s",
     xlab = "Tempo (BPM)",
       border="black", 
     col="blue", 
     xlim=c(50,250),
    ylim = c(0, 60),
     freq = TRUE)
     
nineties_hista<-
 hist(nineties$tempo, main = "Tempi in the 90s",  xlab = "Tempo (BPM)",
      border="black", 
     col="blue", 
     xlim=c(50,250),
     ylim = c(0, 60),
     freq = TRUE)

zeroes_hista<- 
   hist(thousands$tempo, main = "Tempi in the 00s",  xlab = "Tempo (BPM)",
        border="black", 
     col="blue", 
     xlim=c(50,250),
     ylim = c(0, 60),
     freq = TRUE)

tens_hista<-
   hist(tens$tempo, main = "Tempi in the 10s", xlab = "Tempo (BPM)",
        border="black", 
     col="blue", 
     xlim=c(50,250),
     ylim = c(0, 60),
     freq = TRUE,)




```


### Tempi Popular Songs 
```{r, one_analysis}


shame70s <-
  get_tidy_audio_analysis("1l1YTy9nJ0trwhsCGcimly")

happy80s <-
  get_tidy_audio_analysis("5YbgcwHjQhdT1BYQ4rxWlD")


```

```{r, tempograms}

shame70s %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()


happy80s %>%
  tempogram(window_size = 8, hop_size = 1, cyclic = TRUE) %>%
  ggplot(aes(x = time, y = bpm, fill = power)) +
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +
  labs(x = "Time (s)", y = "Tempo (BPM)") +
  theme_classic()


```

*** 
We'll be looking at two outliers in the form of tempograms.On the left a tempogram of an outlier (relatively high BPM in the seventies): It's a Shame  by the Spinners.On the right a tempogram of an outlier (relatively slow in the eighties): Don't Worry Be Happy by Bobby McFerry

### Histogram


```{r, histos, echo=FALSE}
sixties_hist<- 
hist(sixties$energy, main = "Energy in the 60s",
     xlab = "Energy Level",
     border="black", 
     col="purple", 
     xlim=c(0,1),
     ylim = c(0, 3),
     freq = FALSE)

seventies_hist<-
  hist(seventies$energy, main = "Energy in the 70s",  xlab = "Energy Level",
       border="black", 
     col="purple", 
     xlim=c(0,1),
    ylim = c(0, 3),
     freq = FALSE)

eighties_hist<-
   hist(eighties$energy, main = "Energy in the 80s",  
     xlab = "Energy Level",
       border="black", 
     col="purple", 
     xlim=c(0,1),
    ylim = c(0, 3),
     freq = FALSE)
     
nineties_hist<-
 hist(nineties$energy, main = "Energy in the 90s",  xlab = "Energy Level",
      border="black", 
     col="purple", 
     xlim=c(0,1),
    
     ylim = c(0, 3),
     freq = FALSE)

zeroes_hist<- 
   hist(thousands$energy, main = "Energy in the 00s",  xlab = "Energy Level",
        border="black", 
     col="purple", 
     xlim=c(0,1),
    
     ylim = c(0, 3),
     freq = FALSE)

tens_hist<-
   hist(tens$energy, main = "Energy in the 10s", xlab = "Energy Level",
        border="black", 
     col="purple", 
     xlim=c(0,1),
    
     ylim = c(0, 3),
     freq = FALSE,)


     

```


***
Here we have a clear view of the frequency of every energy level of every song in each playlist. This puts us one step closer to deciding which decade was the "Party Decade".




### Chordogram/Keygram

I'm still standing - Elton John

```{r, ISS, echo=FALSE}
ISS <-
  get_tidy_audio_analysis("0lzpfrTARexLFXEACKSXTh") %>% # Change URI.
  compmus_align(bars, segments) %>%                     # Change `bars`
  select(bars) %>%                                      #   in all three
  unnest(bars) %>%                                      #   of these lines.
  mutate(
    pitches =
      map(segments,
        compmus_summarise, pitches,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  ) %>%
  mutate(
    timbre =
      map(segments,
        compmus_summarise, timbre,
        method = "rms", norm = "euclidean"              # Change summary & norm.
      )
  )

keygram <- ISS %>% 
  compmus_match_pitch_template(
    key_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) + ggtitle("Keygram: 'I'm Still Standing'") +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "Keys") 

chordogram <- ISS %>% 
  compmus_match_pitch_template(
    chord_templates,         # Change to chord_templates if descired
    method = "euclidean",  # Try different distance metrics
    norm = "manhattan"     # Try different norms
  ) %>%
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)
  ) + ggtitle("Chordogram: 'I'm Still Standing'") +
  geom_tile() +
  scale_fill_viridis_c(guide = "none") +
  theme_minimal() +
  labs(x = "Time (s)", y = "Chords")
grid.arrange(keygram, chordogram)

```

***
These are the Keygram and Chordogram from one of the outliers. I haven't had the chance to compare these to other songs from my Corpus.



### Chroma/Cepstrograms



I'm Still Standing - Elton John
Self similarities




```{r, issgrams}
ISS %>%
  compmus_self_similarity(timbre, "aitchison") %>% 
  ggplot(
    aes(
      x = xstart + xduration / 2,
      width = xduration,
      y = ystart + yduration / 2,
      height = yduration,
      fill = d
    )
  ) +
  geom_tile() +
  coord_fixed() +
  scale_fill_viridis_c(guide = "none") +
  theme_classic() +
  labs(x = "Time (s)", y = "Time (s)")

```

```{r, issmoregrams}
ISS %>%
  compmus_gather_timbre() %>%
  ggplot(
    aes(
      x = start + duration / 2,
      width = duration,
      y = basis,
      fill = value
    )
  ) +
  geom_tile() +
  labs(x = "Time (s)", y = NULL, fill = "Magnitude") +
  scale_fill_viridis_c() +                              
  theme_classic()

```



### Graphs/Visuals









```{r, allplots}
  all_plots <-
  top20 %>%  
  ggplot(                          # Set up the plot.
    aes(
      x = energy,
      y = danceability,
      colour = mode,
      size = track.popularity,
      label = track.name           # Labels will be interactively visible.
    )
  ) +
  geom_point(shape = ".") +                   # Scatter plot.
  geom_rug(size = 0.1) +           # Add 'fringes' to show data distribution.
  facet_wrap(~country) +           # Separate charts per country.
  scale_x_continuous(              # Fine-tune the x axis.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),        # Use grid-lines for quadrants only.
    minor_breaks = NULL            # Remove 'minor' grid-lines.
  ) +
  scale_y_continuous(              # Fine-tune the y axis in the same way.
    limits = c(0.5, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_viridis_c(          # Use the cividis palette
    option = "C",                  # Qualitative set.
    alpha = 0.8,                   # Include some transparency
    guide = "none"
  ) +
  scale_size_continuous(           # Fine-tune the sizes of each point.
    guide = "none"                # Remove the legend for size.
  ) +
  theme_classic() +                  # Use a simpler theme.
  labs(                            # Make the titles nice.
    x = "Energy",
    y = "Danceability"
  )
ggplotly(all_plots)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

                  
```

